{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2021-01-26 documents/supplemental.tex
still broken sources
Dialogue
More discussion
Progress on RPi cal

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\Huge Captain's Log, Supplemental}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{fquote}[Paraphrased from W. G. Cochran][\cite{Statistical1953}]
The accumulated insight of a worker frequently merits recording when no documentation can be given.
\end{fquote}

@@

@@

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\Large Microwave Musings}\\
\begin{multicols}{1}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

>>>>

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Appendix]{\Huge Captain's Log, Supplemental}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{fquote}[Paraphrased from W. G. Cochran][\cite{Statistical1953}]
The accumulated insight of a worker frequently merits recording when no documentation can be given.
\end{fquote}

%tonsil

@@

Rationale for doing this alone. Science is nothing without collaboration. However, it's also nothing without acknowledging the shortfalls of your research. There remains no physical reason to expect this to work - it is indistinguishable from crackpottery - and, in fact, the first route of investigation did not work. Therefore, seemed irresponsible to redirect resources or involve other people.

at least that's the story I tell myself.

@@

\clearpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\Large Microwave Musings}\\

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

many programs try to implement their own command scripting language
if the api doesn't expose access to the data on each timestep, then you're limited to the features that have already been implemented
